### 2022-12-01 abstract.tex
suggestions from Charlotte

The first and largest part of this thesis extends a recently proposed
reverse-Bayes method for quantifying replication success. The key idea is to
challenge the data from the original study with a sceptical prior so that the
resulting posterior no longer provides evidence for the finding from the study.
While the proposed method defined evidence through tail probabilities, the
extension developed here replaces them with Bayes
factors. % The sceptical prior is now
% determined such that the original finding is no longer convincing in terms of a
% Bayes factor. In contrast to tail probabilities,
We find that the extended method combines two notions of replicability: It
requires that original and replication study independently provide evidence for
an effect and ensures that their effect estimates are compatible. The extended
method also avoids a statistical paradox which the proposed method suffered
from.
% Bayes factors have a more
% natural interpretation and allow for direct quantification of evidence for one
% hypothesis versus another. As with the sceptical $p$-value, the procedure leads
% to a single measure quantifying the degree of replication success called the
% sceptical Bayes factor.
Another extension proposed in this thesis recalibrates the proposed method to
produce more appropriate inferences in terms of effect
size. % from the relative effect size
% perspective
The recalibration is chosen such that for original studies which were borderline
significant, replication success can only be achieved if the replication effect
estimate is larger than the original one. The recalibrated method has good
frequentist properties comparable to standard methods used in practice. The
third and last extension provides a framework for Bayesian design of replication
studies which allows for combining data from the original study with external
knowledge. External knowledge, such as data from other studies, is ubiquitous in
the replication setting and taking it into account can potentially lead to more
efficient designs compared to classical approaches.

The second part of the thesis is concerned with reverse-Bayes methodology. The
reverse-Bayes idea was first proposed in the 1950s, but it has mostly been
forgotten. To increase awareness and show potential use cases, reverse-Bayes
history and methods are summarized in a comprehensive review. The review
includes also some new results on connections between revere-Bayes methods and
meta-analysis. Finally, a commentary paper on a recently proposed reverse-Bayes
method draws connections to other reverse-Bayes methods.

>>>>

The first and largest part of this thesis consists of three extensions of a
recently proposed reverse-Bayes method for quantifying replication success. The
key idea of the method is to challenge the data from the original study with a
sceptical prior so that the resulting posterior no longer provides evidence for
the finding from the study. The first extension recalibrates the proposed method
to produce more appropriate inferences in terms of effect size.
% from the relative effect size perspective
The recalibration is chosen such that for original studies which were borderline
significant, replication success can only be achieved if the effect estimate
from the replication study is larger than the estimate from the original study.
The recalibrated method has good frequentist properties comparable to standard
methods used in practice. The second extension replaces tail probabilities with
Bayes factors as measures of evidence.
% The sceptical prior is now determined such that the original finding is no
% longer convincing in terms of a Bayes factor. In contrast to tail
% probabilities,
We find that the extended method combines two notions of replicability: It
requires that original and replication study independently provide evidence for
an effect and ensures that their effect estimates are compatible. The extended
method also avoids a statistical paradox which the initial method suffered from.
% Bayes factors have a more
% natural interpretation and allow for direct quantification of evidence for one
% hypothesis versus another. As with the sceptical $p$-value, the procedure leads
% to a single measure quantifying the degree of replication success called the
% sceptical Bayes factor.
The third and last extension provides a framework for Bayesian design of
replication studies which allows for combining data from the original study with
external knowledge. External knowledge, such as data from other studies, is
ubiquitous in the replication setting and taking it into account can potentially
lead to more efficient designs compared to classical approaches.

The second part of the thesis is also concerned with reverse-Bayes methodology
but with a wider ranger of applications than only replication studies. The
reverse-Bayes idea was first proposed in the 1950s, but it has mostly been
forgotten. To increase awareness and show potential use cases, reverse-Bayes
history and methods are summarized in a comprehensive review. The review
includes also some new results on connections between revere-Bayes methods and
meta-analysis. Finally, a commentary paper on a recently proposed reverse-Bayes
method draws connections to other reverse-Bayes methods.
